\begin{abstract}
Cyber-Physical Systems (CPSs) were a synthesis, and a complex system has become consensus. The collaborative design is a potential approach to deal with the rise of the complexity of system design which attracts more and more attention. It relied on Model-driven engineering (MDE) with involving several modeling languages (such as SysML, AADL, etc.) and using principles of separation of concerns as well as domain-specific languages (DSL). It makes stakeholders from diverse domains to work in a coordinated manner on different aspects of the system. It could help in reducing the gap between heterogeneous domains and making diverse expertise work together to produce a coherent and complete system. Therefore, there is a need for collaborative platforms to allow modelers to work together. We proposed a new approach to blending different languages seamlessly by manipulating metamodel with a set of transformation operators at the high-level and early stage of development. The process starts from a SysML system model, developed according to the platform-based design (PBD) paradigm, in which a functional model of the system (SW) is paired to a model of the execution platform (HW). Subsystems are refined as AADL models. In turn, AADL models are implemented as code and transfer to model-checker to perform verification and validation respectively. We illustrate our approach with an experimental of (engine??) design processes represented as scenarios.


 
%The development of complex software-intensive systems requires stakeholders from diverse domains to work in a coordinated manner on different aspects of the system. Model-driven engineering (MDE) helps in reducing the gap between heterogeneous domains using principles of separation of concerns, automatic generation and domain-specific languages (DSL). MDE is thus a potential solution to help develop systems collaboratively. In MDE, stakeholders work on models in order to design, transform, simulate, and analyze systems. Teams of stakeholders with varying expertise work together to produce a coherent and complete system. Therefore, there is a need for collaborative platforms to allow modelers to work together.
%we present the different research projects we have been working on in the topic of collaborative modeling in MDE. After laying a set of necessary requirements I address several topics. We will look at the data structures needed to ensure near real-time collaboration. We will see how multi-view modeling is essential to let users work on different aspects of the system concurrently. Having users from different domains and expertise, we show how to adapt the modeling environment specifically to the needs and habits of the user. We will discuss automatic generation of restrictive modeling IDEs that can support all sorts of user interaction modes.


\end{abstract} 
