\section{Operators}
\subsection{Definition of aspect model}
A system includes a series of aspects and each aspect consist of several metamodels. We defined a aspect model as a 3-tuple, it contains abstract syntax, semantics, and model type:
\begin{center}
	$AS \circeq \langle S_{abs}, Sem, M_{t}\rangle $
\end{center}
where $S_{abs}$ is abstract syntax of the language that is described the aspect model as a language, it could be any modeling language that we usually used such as SysML. $Sem$ is semantics. $M_{t}$ is exact model type. For non-ambiguous reason, we simply denote them as  $S_{abs}, Sem, M_{t}$.

The abstract syntax $S_{abs}$ is at the high-level (M3) in MOF hierarchical system. we specify abstract syntax as metamodel.   

\subsection{(Composited Component)}

From overall point of view, the aspect consist of a set of relevant elements,  

\subsection{allocation}
In SysML, Allocate is a mechanism to associate elements of the different type or in different hierarchies. It is also a stereotype of a UML4SysML:: Abstraction that is used between any two namedElements and dedicates to enabling allocations to identify the sources and targets. (\textbf{see figure}) 

AADL is an architecture language for the specification, analysis, automated integration and code generation when describing real-time computational systems. The Architecture Analysis \& Design Language (AADL) was approved and published as SAE Standard AS-5506 in November 2004. In AADL, the model is designed by using predefined components such as type and implementation declarations  [9]. An AADL system model is able to describe the architecture and runtime environment of an application system. Its component software and execution platforms usually for hardware components are described by component and connection. AADL support mode change to express the evolution of system such as cheddar. AADL provides annex for core language of AADL which can extend the description capacity of AADL (e.g., error annex or behavior annex). In AADL toolset environment, textual specification, XML specification, and graphical notation are all supported.

The AADL has defined software components and execution platform components. specify which processor schedules and executes a thred, and memeory components in which executable code (process components) and data reside.

\defn{(Functional MM)} we denote 




%Ideally, all aspects play a equally important role, In practice however, one often chosen a base model as backbone on which other aspects are woven.  
%\subsection{Merging Models}
%To merge two models (Metamodels), we ought have one entry point whom is \textit{pointcut},  

%$<\mathring{A_s}, \wideparen{Sem}, CP, A_d>$, which $\mathring{A_s}$

We denote $sig$ the signature of an aspect $\mathcal{A}$. The signature of an aspect is a metamodel that describes all the features (\textit{i.e.}parametres, properties) defined.